Data-Driven Search-based Software Engineering

### 2018-01-29 doc/tex/msr18/main.tex
Ready V1

As a field evolves, so too should its canonical problems. One  reason for the emergence of   MSR  in 2004 was the existence of a new generation of widely-available data mining
algorithms that could scale to interestingly large problems. In this paper,
we pause to reflect on what other kinds of algorithms are widely available and could
be applied to MSR problems.  Specifically, we focus on
{\em search-based software engineering} (SBSE) algorithms. Whereas:
\begin{itemize}
\item
An MSR researcher might deploy a
data miner to learn a model from  data   that predicts for (say) a single target class;
\item
An SBSE researcher might deploy a multi-objective optimizer
to find what {solutions} score best
on multiple target variables.
\end{itemize}

@@

{The similar goals of these two areas, as well as the intrinsic relationship between data mining and optimization algorithms, has been recently inspiring an} increase in methods that combine MSR and SBSE.
A recent {NII Shonan Meeting}  on {\em Data-driven Search-based Software
Engineering} (goo.gl/f8D3EC)   was well attended by over two dozen senior members of the MSR community.
The workshop concluded that (1) mining software repositories could be improved using {tools from the SBSE community}; and that (2) search-based methods can be improved using tools from the MSR community. 
For example:
\begin{itemize}
\item
MSR data mining algorithms can be used to summarize the data, after which SBSE can leap to better solutions, faster~\cite{krall2015gale}.
\item
SBSE {algorithms} can be used to intelligently select 
settings for MSR data mining algorithms (e.g.
such as how many trees should be included in a random
forest~\cite{fu2016tuning}).
\end{itemize}
The workshop also concluded that this community needs more shared  resources 
to help more researchers and educators explore MSR+SBSE.
Accordingly, this paper describes  tiny.cc/sbse,
a collection of artifacts for exploring
data-driven search-based SE (see Figure~1). 
All the materials in this repository
have been used in recent SE papers; i.e., for all this material, there exist baseline results against which researchers can use to comparatively assess their new ideas.
%\TODO{Re: fig. 1, are we allowed to use Abhaham's nice piece of art?}

@@

                % \multicolumn{3}{c}{\rowcolor{gray}\textcolor{white}{\textbf{}}} \\ 
                \rowcolor{gray}\textcolor{white}{\textbf{Features}} & \hspace{2cm}\textcolor{white}{\textbf{MSR}} & \hspace{3cm}\textcolor{white}{\textbf{SBSE}} \\ 
                 \rowcolor{gray!30} \textbf{Primary inference} & Induction, summarization, visualization & Optimization \\
                \textbf{Inference speed} & Very fast, scalable & Becoming faster, more scalable\\
                 \rowcolor{gray!30}\textbf{Data} often collected &
                 Once,  then processed.
                &
                On-demand
                from  some model---which means an SBSE analysis can 
                generate new samples of the data in very  specific regions.
                \\ 
                \textbf{Conclusions} often 
                generated via
                &
                A single  execution of a data miner or an ensemble, 
                perhaps after some data pre-processing. 
                &
                An evolutionary process  where, many times, execution $i+1$ is guided
                by the results of execution $i$.
                \\

                 \rowcolor{gray!30}\textbf{Canonical   tools} are usually
                &
                Data mining algorithms like  the decision
                tree learners of WEKA~\cite{hall2009weka} or the mathematical modeling tools of R~\cite{rmanual18} or Scikit-learn~\cite{scikit-learn}.
                &
                {Search-based} optimization algorithms which may be either home-grown scripts or parts of large toolkits such as jMETAL\cite{refs2jmetalDEE}, Opt4j~\cite{opt4jpaper}, DEAP~\cite{DEAP_JMLR2012}.
                \\ 
                \textbf{Canonical   problems}
                &
                Defect prediction~\cite{lessmann2008benchmarking}   or Stackoverflow text mining~\cite{fu2017easy}. 
                &
                Minimizing a test suite~\cite{fraser2007redundancy}, configuring a software system~\cite{nair2017faster} or extracting a valid products from a product line description~\cite{sayyad13b}.
                % or selecting screen designs that
                % reduce the power consumption  mobile devices
                \\

                 \rowcolor{gray!30} \textbf{Results}   assessed by
                &
                A small number of standard measures
                including   recall, precision, or false alarm rates (for discrete classes)
                or magnitude of relative error (for continuous classes)~\cite{Shepperd2012}.
                &
                A wide-variety of domain-specific objectives.
                Whatever the specific objectives, a small number meta-measures are used in many research papers such as the Hypervolume or Spread. 
    \end{tabular}
    \caption{Differences between Software Analytics and Search-based Software Engineering}
    \label{fig:diff}
\end{figure*}

@@

As to defining {\em data-driven search-based SE},
we say it is some system that:
\begin{itemize}
\item To solve  some SE problem:
\begin{itemize}
\item
It inserts  a data miner into an optimizer; or
\item
It uses an optimizer  to improve a data  miner.
\end{itemize}
\end{itemize}

@@

Not only is   MSR useful for   SBSE, but so too:
\begin{quote}
\centering
{\bf {\em SBSE methods can    ``supercharge''    MSR.}}
\end{quote}
The standard example here is parameter tuning. Most data mining algorithms come with tuning
parameters that have to be set via expert judgment. Much recent work shows that for
MSR problems such as defect prediction and text mining, SBSE can automatically find settings that are far superior to the default settings. For example:
\begin{itemize}
 \item
   When performing defect prediction, various groups report that SBSE methods can find new settings that dramatically improve the performance of the learned model~\cite{fu2016tuning,tantithamthavorn2016automated, Tantithamthavorn2018}.

@@

\noindent\textbf{Strategy: } The problem of finding the (near) optimal configuration is expensive and often infeasible using the current techniques. A useful strategy could be to build a machine learning model which can differentiate between the good and not so good solutions. Flash, a Sequential Model-based Optimization (SMBO), is a useful
strategy to find extremes of an unknown objective. Flash is
efficient because of its ability to incorporate prior belief as
already measured solutions (or configurations), to help direct
further sampling. Here, the prior represents the already
known areas of the search (or performance optimization) problem. The prior can be used to estimate the rest of the
points (or unevaluated configurations). Once one (or many) points are evaluated based on the prior,
the posterior can be defined. The posterior captures the updated belief in
the objective function. This step is performed by using a
machine learning model, also called surrogate model. 
The concept of Flash can be simply stated as:
\begin{itemize}
\item Given what one knows about the problem,
\item what can be done next?
\end{itemize}
The ``given what one knows about the problem'' part is
achieved by using a machine learning model whereas ``what can be done next'' is performed by an acquisition function.
Such acquisition function automatically adjusts the exploration
(``should we sample in uncertain parts of the search
space'') and exploitation (``should we stick to what is already
known'') behavior of the method. Please refer to  \cite{nair2018finding} and  \cite{nair2017using,nair2017faster, jamshidi2016uncertainty} to similar strategies. The reproduction package is available in \censor{\url{http://tiny.cc/flashrepo/}}.

@@

    \noindent\textbf{Problem:} The process of building and analyzing complex requirements engineering models can help stakeholders better understand the ramifications of their decisions~\cite{Lamsweerde2001,amyot10}. But models can sometimes overwhelm stakeholders. For example, consider a committee reviewing a goal model (see fig. \ref{fig:csServices}) that describes the information needs of a computer science department~\cite{Horkoff2016}. Although the model is entangled, on manual and careful examination, it can be  observed that much of the model depends on a few ``key'' decisions such that once their values are assigned, it becomes very simple to reason over the remaining decisions. It is beneficial to look for these ``keys'' in requirements models since, if they exist, one can achieve ``shorter'' reasoning about large RE models, where ``shorter'' is measured as follows:
    \begin{itemize}
     \item{Large models can be processed in a very short time.}
     \item{Runtimes for automatic reasoning about RE models are shorter so stakeholders can get faster feedback on their models.}
     \item{The time required for manual reasoning about models is shorter since stakeholders need only debate a small percent of the issues (just the key decisions).}
    \end{itemize}

@@

\noindent\textbf{Strategy:} To overcome this problem, a technique called SHORT was proposed, which runs in four phases:
\begin{itemize}
    \item{\textbf{SH}: 'S'ample 'H'euristically the possible labelings of the model.}
    \item{\textbf{O}: 'O'ptimize the label assignments to cover more goals or reduce the sum of the cost of the decisions in the model.}
    \item{\textbf{R}: R: 'R'ank all decisions according to how well they performed during the optimization process.}
    \item{\textbf{T}: T: 'T'est how much conclusions are determined by the decisions that occur very early in that ranking.}
\end{itemize}

@@

\subsection{FASTREAD}
\noindent\textbf{Problem Domain: } SBSE

@@

@@

\noindent\textbf{Strategy: }
  Reading all   literature  is unfeasible. Active learners incrementally learns from the human feedback and suggests on which paper to review next.

\vspace{1.0ex}
\noindent\textbf{Challenge 2: }
A wrong choice of initial papers can increase the review effort by up to 300\% than the median effort (repeat for 30 runs)---requires three times more effort to retrieve the relevant papers.

\noindent\textbf{Strategy: }
Reduce  variances  by selecting a good initial set of papers with domain knowledge from the researcher. We found that by ranking the papers with some  keywords (provided as domain knowledge) and reviewing in such order, the effort can be   reduced with negligible variances.

@@

\noindent\textbf{Strategy: }
Use a semi-supervised machine learning algorithm (Logistic Regression) to learn from the search process (till now) to predict how much more relevant paper will be found.

@@

\noindent\textbf{Strategy: }
Concentrate the effort on correctly classifying the paper which creates the most controversy. Using this intuition, periodically few of the already evaluated papers, whose labels the active learner disagree most on, are re-evaluated.

@@

\noindent\textbf{Problem: } Stack Overflow is a popular Q\&A website, where users posts the questions and the community collectively answers these questions. However, as the community evolves, there is chance that duplicate questions can appear---which results in a wasted effort of the community. There is a need to remove the duplicate question or consolidate related questions. The problem focuses on discovering the relationship between any two questions posted on Stack Overflow and classifies them into duplicates, direct link, indirect link, and isolated~\cite{fu2017easy, xu2016predicting}. One way to solve this problem is to build a predictive model which can predict the similarity between two questions.

@@

Grid computing techniques, invented in the mid-1990s, as well as recently lots of pay-as-you-go cloud computing services, e.g., Amazon EC2, provide researchers a feasible way to finish such kind of complex workflow in a reasonable time.
The workflow configuring problem is to figure out the best deployment configurations onto a cloud environment. The deployment configuration
contains 1) determine which sub-tasks can be deployment into
one computation node, i.e., the virtual machine in cloud environment; 2) which sub-task should be executed first if two of them are to be executed in the same node; 3) what hardware configuration (CPU, memory, bandwidth, etc.) should be applied in each computation node. Commercial cloud service provider charges users for computing resource. 
The objective of cloud configuration is to minimize the monetary cost as well as minimize the runtime of computing tasks.

\noindent\textbf{Challenges: } 
Two reasons make workflow configuration on cloud environment challenging: 1)  a number of sub-tasks of workflows can be as large as hundreds, or thousands; also, sub-tasks is under constraints-- file flow between them. 2) available types of
computing nodes from cloud service provided is huge.
For example, Amazon AWS provides more than 50 types of virtual machines; these
virtual machines have different computing ability, as well as unit price (from \$0.02/hr to \$5/hr).
Given these two reasons,
the configuration space, or a number of possible deployment ways, is huge.
Even though modern cloud environment simulator, such as CloudSim, can quick
access performance of one deployment, evaluate every
possible deployment configuration is impossible.

\noindent\textbf{Strategy:} 
Since it is impossible to enumerate all possible configurations, most existed algorithm use either 1) greedy algorithm 2) evolutionary algorithm to figure out best configurations.
Similar to other search-based software engineering problems,
these methods require a large number of model evaluations (simulations in workflow configuration problem).
The RIOT, or randomized instance-order-type, is an algorithm to balance execution time as well as cost
in a short time.
The RIOT first groups sub-tasks, making the DAG simpler, and then
assign each group into one computation node. Within one node,
priorities of sub-tasks are determined by
B-rank~\cite{topcuoglu2002performance}, a greedy algorithm. 
The most tricky part is to determine types of computation nodes so that they can coordinate with each other and reduce the total ideal time (due to file transfer constraints).
RIOT makes full use of two hypothesis: (1) similar configurations should have similar performance and (2) (monotonicity) k times computing resource should lead to (1/k)*c less computation time (where c is constant for one workflow).
With these two hypotheses,
RIOT first randomly creates some deployment configurations and evaluates them, then guess more configurations based on current evaluated configuration. Such kind of guess can avoid a large number of configuration evaluations. Please refer to \cite{chen2017riot} for more details and the reproduction package is available in \censor{\url{http://tiny.cc/raise_gen_workflow}}.

@@

\noindent\textbf{Learning: } To learn SBSE, coding up a Simulated Annealer~\cite{van1987simulated} and Differential Evolution (DE)~\cite{storn97} is a good starting point.  These algorithms work really well for single-objective problems. For multi-objective problems, one should code up binary domination and indicator domination~\cite{zitzler2001spea2}. Note that the indicator domination is recommended for N>2 objectives and that indicator domination along with DE is a simple way to get a wide spread of solutions on the PF.

As to learning more about area, the popular venues are: 
\begin{itemize}
\item \href{http://gecco-2018.sigevo.org/index.html/HomePage}{GECCO}: The Genetic and Evolutionary Computation Conference (which has a special SE track);
\item \href{http://ieeexplore.ieee.org/xpl/RecentIssue.jsp?punumber=4235}{IEEE Transactions on Evolutionary Computation}
\item SSBSE: the annual symposium on search-based SE;
\item Recent papers   as FSE, ICSE, ASE, etc: \url{goo.gl/Lvb42Z};
\item Google Scholar: see  \url{goo.gl/x44u77}
\end{itemize}
  \noindent\textbf{Debugging: } It is always recommended to use small and simple {optimization problems} for the purposes of debugging. For example, small synthetic {problems} like ZDT, DTLZ~\cite{deb2005scalable}, and WFG~\cite{huband2006review} are very useful to evaluate a meta-heuristic algorithm. For further details about other test problems, please refer to \cite{huband2006review}.

@@

\noindent\textbf{Choosing Algorithm and its parameters: } {Choosing the meta-heuristic algorithm to solve a particular problem can be often challenging. Although, the chosen algorithm is generally a preference of the researcher, it is commonly agreed to use algorithms such as NSGA-II or SPEA2 for problems with $<3$ objectives whereas NSGA-III and MOEA/D is preferred for problems with $>3$ objectives.}

@@

 \noindent\textbf{Experimentation: } We recommend an experimentation technique called (you+two+next+dumb),  defined as 
\begin{itemize}
\item ``you'' is your new method;
    \item ``two''  well-established methods (often NSGA-II and SPEA2),
    \item a ``next''  generation method e.g. MOEA/D~\cite{zhang2007moea}, NSGA-III~\cite{deb2014evolutionary},
    \item  one ``dumb'' baseline method (random search or SWAY).
\end{itemize}

@@

Along with increasing the confidence of a certain observation, it also increases the speed of research. For example, recently in FSE'17 Fu et al.~\cite{fu2017revisiting} described the effects of \textit{arxiv.org} or the open science effect. Fu et al. described how making the paper, and the replication packages results in 5 different techniques (each superior to its predecessor).\footnote{Please see \url{http://tiny.cc/unsup}  for more details on arxiv.org effect}

@@

  \noindent\textbf{Explanation: } SBSE is often instance-based and provide optimal or (near) optimal solutions. This is not ideal since it provides no insight into the problem. However, using SA techniques finding
building blocks of good solutions may shed light on the relationship
different parameters that affect the quality of a solution. This is an important shortcoming of SBSE which have not been addressed by this community. Valerdi
notes that, without automated tools, it can take days for human
experts to review just a few dozen examples. In that same
time, an automatic tool can explore thousands to billions of more
solutions. Humans can find it an overwhelming task just to
certify the correctness of conclusions generated from so many
results. Verrappa and Leiter warn that:
``... for industrial problems, these algorithms generate
(many) solutions which make the task of understanding
them and selecting one amongst them difficult
and time-consuming.''~\cite{veerappa2011understanding}. Currently, there has been only a few efforts to comprehend the results of an SBSE technique. Nair et al.~\cite{nair2017flash}, described FLASH, which
combines   how a \textit{domination tree} along with a Bayesian-based method to better, and more succinctly,
explain the search space.

 \noindent\textbf{Human in the loop: } Once we have explanation running, then the next step would be explore
combinations of human and artificial intelligence for
enhanced data-driven SBSE.
Standard
genetic algorithms must evaluate 1000s to 1,000,000s of examples-- which makes it hard for engineers or business users to debug or audit the results of that analysis. On the 
other hand, tools like FLASH (described in the last bullet)
and SWAY (see Section \ref{spl}) only evaluated $O(log(N))$ of the candidates-- which in practice can be just a few dozen examples. This number is small enough to ask humans
to watch the reasoning and, sometimes, catch the SBSE
tool making mistakes as it compares alternatives.  This style of human in the loop reasoning could be used for many tasks such as:
\begin{itemize}[leftmargin=*]
\item Debugging or auditing the reasoning.
\item Enhancing the reasoning; i.e. can human intelligence, applied judiciously,  boost artificial intelligence?
\item Checking for missing attributes: when human experts say two identical examples are different, we can infer that there are extra attributes, not currently being modeled, that are important in this domain.
\item Increasing human  confidence in the reasoning by tuning a seemingly complex black-box process into something
humans can monitor and understand.
\end{itemize}

@@

\section{Conclusions}
Software engineering problems can be solved both by MSR and SBSE techniques, but both these methods have their shortcomings. This paper has argued these shortcomings can be overcome by merging ideas from both these domains, to give rise to a new field of software engineering called Data-Driven Search-based Software Engineering. This sub-area of software engineering boosts the techniques used in MSR and SBSE but drawing inspiration from the other field.

>>>>

As a field evolves, so too should its canonical problems. One  reason for the emergence of   MSR  in 2004 was the existence of a new generation of widely-available data mining
algorithms that could scale to interestingly large problems. In this paper,
we pause to reflect on what other kinds of algorithms are widely available and could
be applied to MSR problems.  Specifically, we focus on
{\em search-based software engineering} (SBSE) algorithms. Whereas:
\begin{itemize}[leftmargin=*]
\item
An MSR researcher might deploy a
data miner to learn a model from  data   that predicts for (say) a single target class;
\item
An SBSE researcher might deploy a multi-objective optimizer
to find what {solutions} score best
on multiple target variables.
\end{itemize}

@@

{The similar goals of these two areas, as well as the intrinsic relationship between data mining and optimization algorithms, has been recently inspiring an} increase in methods that combine MSR and SBSE.
A recent {NII Shonan Meeting}  on {\em Data-driven Search-based Software
Engineering} (goo.gl/f8D3EC)   was well attended by over two dozen senior members of the MSR community.
The workshop concluded that (1) mining software repositories could be improved using {tools from the SBSE community}; and that (2) search-based methods can be improved using tools from the MSR community. 
For example:
\begin{itemize}[leftmargin=*]
\item
MSR data mining algorithms can be used to summarize the data, after which SBSE can leap to better solutions, faster~\cite{krall2015gale}.
\item
SBSE {algorithms} can be used to intelligently select 
settings for MSR data mining algorithms (e.g.
such as how many trees should be included in a random
forest~\cite{fu2016tuning}).
\end{itemize}
The workshop also concluded that this community needs more shared  resources 
to help more researchers and educators explore MSR+SBSE.
Accordingly, this paper describes  tiny.cc/sbse,
a collection of artifacts for exploring
data-driven search-based SE (see Figure~1). 
All the materials in this repository
have been used in recent SE papers; i.e., for all this material, there exist baseline results against which researchers can use to comparatively assess their new ideas.
%\TODO{Re: fig. 1, are we allowed to use Abhaham's nice piece of art?}

@@

                % \multicolumn{3}{c}{\rowcolor{gray}\textcolor{white}{\textbf{}}} \\ 
                \toprule
                \textbf{Features} & \hspace{2cm}\textbf{MSR} & \hspace{3cm}\textbf{SBSE} \\ \midrule
                \rowcolor[HTML]{EFEFEF} \textbf{Primary inference} & Induction, summarization, visualization & Optimization \\
                \textbf{Inference speed} & Very fast, scalable & Becoming faster, more scalable\\
                \rowcolor[HTML]{EFEFEF}\textbf{Data} often collected &
                 Once,  then processed.
                &
                On-demand
                from  some model---which means an SBSE analysis can 
                generate new samples of the data in very  specific regions.
                \\ 
                \textbf{Conclusions} often 
                generated via
                &
                A single  execution of a data miner or an ensemble, 
                perhaps after some data pre-processing. 
                &
                An evolutionary process  where, many times, execution $i+1$ is guided
                by the results of execution $i$.
                \\

                \rowcolor[HTML]{EFEFEF}\textbf{Canonical   tools} are usually
                &
                Data mining algorithms like  the decision
                tree learners of WEKA~\cite{hall2009weka} or the mathematical modeling tools of R~\cite{rmanual18} or Scikit-learn~\cite{scikit-learn}.
                &
                {Search-based} optimization algorithms which may be either home-grown scripts or parts of large toolkits such as jMETAL\cite{refs2jmetalDEE}, Opt4j~\cite{opt4jpaper}, DEAP~\cite{DEAP_JMLR2012}.
                \\ 
                \textbf{Canonical   problems}
                &
                Defect prediction~\cite{lessmann2008benchmarking}   or Stackoverflow text mining~\cite{fu2017easy}. 
                &
                Minimizing a test suite~\cite{fraser2007redundancy}, configuring a software system~\cite{nair2017faster} or extracting a valid products from a product line description~\cite{sayyad13b}.
                % or selecting screen designs that
                % reduce the power consumption  mobile devices
                \\

                \rowcolor[HTML]{EFEFEF} \textbf{Results}   assessed by
                &
                A small number of standard measures
                including   recall, precision, or false alarm rates (for discrete classes)
                or magnitude of relative error (for continuous classes)~\cite{Shepperd2012}.
                &
                A wide-variety of domain-specific objectives.
                Whatever the specific objectives, a small number meta-measures are used in many research papers such as the Hypervolume or Spread. 
    \end{tabular}
    \caption{Differences between Software Analytics and Search-based Software Engineering}
    \label{fig:diff}
\end{figure*}

@@

As to defining {\em data-driven search-based SE},
we say it is some system that:
\begin{itemize}[leftmargin=*]
\item To solve  some SE problem:
\begin{itemize}
\item
It inserts  a data miner into an optimizer; or
\item
It uses an optimizer  to improve a data  miner.
\end{itemize}
\end{itemize}

@@

Not only is   MSR useful for   SBSE, but so too:
\begin{quote}
\centering
{\bf {\em SBSE methods can    ``supercharge''    MSR.}}
\end{quote}
The standard example here is parameter tuning. Most data mining algorithms come with tuning
parameters that have to be set via expert judgment. Much recent work shows that for
MSR problems such as defect prediction and text mining, SBSE can automatically find settings that are far superior to the default settings. For example:
\begin{itemize}[leftmargin=*]
 \item
   When performing defect prediction, various groups report that SBSE methods can find new settings that dramatically improve the performance of the learned model~\cite{fu2016tuning,tantithamthavorn2016automated, Tantithamthavorn2018}.

@@

\noindent\textbf{Strategy: } The problem of finding the (near) optimal configuration is expensive and often infeasible using the current techniques. A useful strategy could be to build a machine learning model which can differentiate between the good and not so good solutions. Flash, a Sequential Model-based Optimization (SMBO), is a useful
strategy to find extremes of an unknown objective. Flash is
efficient because of its ability to incorporate prior belief as
already measured solutions (or configurations), to help direct
further sampling. Here, the prior represents the already
known areas of the search (or performance optimization) problem. The prior can be used to estimate the rest of the
points (or unevaluated configurations). Once one (or many) points are evaluated based on the prior,
the posterior can be defined. The posterior captures the updated belief in
the objective function. This step is performed by using a
machine learning model, also called surrogate model. 
The concept of Flash can be simply stated as:
\begin{itemize}[leftmargin=*]
\item Given what one knows about the problem,
\item what can be done next?
\end{itemize}
The ``given what one knows about the problem'' part is
achieved by using a machine learning model whereas ``what can be done next'' is performed by an acquisition function.
Such acquisition function automatically adjusts the exploration
(``should we sample in uncertain parts of the search
space'') and exploitation (``should we stick to what is already
known'') behavior of the method. Please refer to  \cite{nair2018finding} and  \cite{nair2017using,nair2017faster, jamshidi2016uncertainty} to similar strategies. The reproduction package is available in \censor{\url{http://tiny.cc/flashrepo/}}.

@@

    \noindent\textbf{Problem:} The process of building and analyzing complex requirements engineering models can help stakeholders better understand the ramifications of their decisions~\cite{Lamsweerde2001,amyot10}. But models can sometimes overwhelm stakeholders. For example, consider a committee reviewing a goal model (see fig. \ref{fig:csServices}) that describes the information needs of a computer science department~\cite{Horkoff2016}. Although the model is entangled, on manual and careful examination, it can be  observed that much of the model depends on a few ``key'' decisions such that once their values are assigned, it becomes very simple to reason over the remaining decisions. It is beneficial to look for these ``keys'' in requirements models since, if they exist, one can achieve ``shorter'' reasoning about RE models, where ``shorter'' is measured as follows:
    \begin{itemize}[leftmargin=*]
     \item{Large models can be processed in a very short time.}
     \item{Runtimes for automatic reasoning about RE models are shorter so stakeholders can get faster feedback on their models.}
     \item{The time required for manual reasoning about models is shorter since stakeholders need only debate a small percent of the issues (just the key decisions).}
    \end{itemize}

@@

\noindent\textbf{Strategy:} To overcome this problem, a technique called SHORT was proposed, which runs in four phases:
\begin{itemize}[leftmargin=*]
    \item{\textbf{SH}: 'S'ample 'H'euristically the possible labelings of the model.}
    \item{\textbf{O}: 'O'ptimize the label assignments to cover more goals or reduce the sum of the cost of the decisions in the model.}
    \item{\textbf{R}: R: 'R'ank all decisions according to how well they performed during the optimization process.}
    \item{\textbf{T}: T: 'T'est how much conclusions are determined by the decisions that occur very early in that ranking.}
\end{itemize}

@@

\subsection{Faster Literature Reviews}
\noindent\textbf{Problem Domain: } SBSE

@@

 Data sets and reproduction packages for all the following are available at \censor{https://doi.org/10.5281/zenodo.837298} (for Challenge~1) and 
\censor{https://doi.org/10.5281/zenodo.1147678} (for Challenges 2,3,4). Please refer to \cite{yu2016finding, YuM17} for more details

@@

\noindent\textbf{Strategy: }
  Reading all   literature  is unfeasible. Active learners incrementally learns from the human feedback and suggests on which paper to review next~\cite{YuM17a}.

\vspace{1.0ex}
\noindent\textbf{Challenge 2: }
A wrong choice of initial papers can increase the review effort by up to 300\% than the median effort (repeat for 30 runs)---requires three times more effort to find   relevant papers.

\noindent\textbf{Strategy: }
Reduce  variances  by selecting a good initial set of papers with domain knowledge from the researcher. We found that by ranking the papers with some  keywords (provided as domain knowledge) and reviewing in such order, the effort can be   reduced with negligible variances~\cite{YuM17}.

@@

\noindent\textbf{Strategy: }
Use a semi-supervised machine learning algorithm (Logistic Regression) to learn from the search process (till now) to predict how much more relevant paper will be found~\cite{YuM17}.

@@

\noindent\textbf{Strategy: }
Concentrate the effort on correctly classifying the paper which creates the most controversy. Using this intuition, periodically few of the already evaluated papers, whose labels the active learner disagree most on, are re-evaluated~\cite{YuM17}.

@@

\noindent\textbf{Problem: } Stack Overflow is a popular Q\&A website, where users posts the questions and the community collectively answers these questions. However, as the community evolves, there is chance that duplicate questions can appear---which results in a wasted effort of the community. There is a need to remove the duplicate question or consolidate related questions. The problem focuses on discovering the relationship between any two questions posted on Stack Overflow and classifies them into duplicates, direct link, indirect link, and isolated~\cite{fu2017easy, xu2016predicting}. One way to solve this problem is to build a predictive model to predict the similarity between two questions.

@@

Grid computing techniques, invented in the mid-1990s, as well as recently lots of pay-as-you-go cloud computing services, e.g., Amazon EC2, provide researchers a feasible way to finish such kind of complex workflow in a reasonable time.
The workflow configuring problem is to figure out the best deployment configurations onto a cloud environment. The deployment configuration
contains (1) determine which sub-tasks can be deployment into
one computation node, i.e., the virtual machine in cloud environment; (2) which sub-task should be executed first if two of them are to be executed in the same node; (3) what hardware configuration (CPU, memory, bandwidth, etc.) should be applied in each computation node. Commercial cloud service provider charges users for computing resource. 
The objective of cloud configuration is to minimize the monetary cost as well as minimize the runtime of computing tasks.

\noindent\textbf{Challenges: } 
Two reasons make workflow configuration on cloud environment challenging: (1)  a number of sub-tasks of workflows can be as large as hundreds, or thousands; also, sub-tasks is under constraints-- file flow between them. (2) available types of
computing nodes from cloud service provided is huge.
For example, Amazon AWS provides more than 50 types of virtual machines; these
virtual machines have different computing ability, as well as unit price (from \$0.02/hr to \$5/hr).
Given these two reasons,
the configuration space, or a number of possible deployment ways, is huge.
Even though modern cloud environment simulator, such as CloudSim, can quick
access performance of one deployment, evaluate every
possible deployment configuration is impossible.

\noindent\textbf{Strategy:} 
Since it is impossible to enumerate all possible configurations, most existed algorithm use either (1) greedy algorithm (2) evolutionary algorithm to figure out best configurations.
Similar to other search-based software engineering problems,
these methods require a large number of model evaluations (simulations in workflow configuration problem).
The RIOT, or randomized instance-order-type, is an algorithm to balance execution time as well as cost
in a short time.
The RIOT first groups sub-tasks, making the DAG simpler, and then
assign each group into one computation node. Within one node,
priorities of sub-tasks are determined by
B-rank~\cite{topcuoglu2002performance}, a greedy algorithm. 
The most tricky part is to determine types of computation nodes so that they can coordinate with each other and reduce the total ideal time (due to file transfer constraints).
RIOT makes full use of two hypothesis: (1) similar configurations should have similar performance and (2) (monotonicity) k times computing resource should lead to (1/k)*c less computation time (where c is constant for one workflow).
With these two hypotheses,
RIOT first randomly creates some deployment configurations and evaluates them, then guess more configurations based on current evaluated configuration. Such kind of guess can avoid a large number of configuration evaluations. Please refer to \cite{chen2017riot} for more details and the reproduction package is available in \censor{\url{http://tiny.cc/raise_gen_workflow}}.

@@

\noindent\textbf{Learning: } To learn SBSE, coding up a Simulated Annealer~\cite{van1987simulated} and Differential Evolution (DE)~\cite{storn97} is a good starting point.  These algorithms work really well for single-objective problems. For multi-objective problems, one should code up binary domination and indicator domination~\cite{zitzler2001spea2}. Note that the indicator domination is recommended for N>2 objectives and that indicator domination along with DE can find a wide spread of solutions on the PF.

As to learning more about area, the popular venues are: 
\begin{itemize}[leftmargin=*]
\item \href{http://gecco-2018.sigevo.org/index.html/HomePage}{GECCO}: The Genetic and Evolutionary Computation Conference (which has a special SE track);
\item TSE: \href{http://ieeexplore.ieee.org/xpl/RecentIssue.jsp?punumber=4235}{IEEE Transactions on Evolutionary Computation};
\item SSBSE: the annual symposium on search-based SE;
\item Recent papers   as FSE, ICSE, ASE, etc: \url{goo.gl/Lvb42Z};
\item Google Scholar: see  \url{goo.gl/x44u77}
\end{itemize}
  \noindent\textbf{Debugging: } It is always recommended to use small and simple {optimization problems} for the purposes of debugging. For example, small synthetic {problems} like ZDT, DTLZ~\cite{deb2005scalable}, and WFG~\cite{huband2006review} are very useful to evaluate a meta-heuristic algorithm. For further details about other test problems, please refer to \cite{huband2006review}.

@@

\noindent\textbf{Choosing Algorithm and its parameters: } {Choosing the meta-heuristic algorithm to solve a particular problem can be often challenging. Although, the chosen algorithm is generally a preference of the researcher, it is commonly agreed to use NSGA-II or SPEA2 for problems with $<3$ objectives whereas NSGA-III and MOEA/D is preferred for problems with $>3$ objectives.}

@@

 \noindent\textbf{Experimentation: } We recommend an experimentation technique called (you+two+next+dumb),  defined as 
\begin{itemize}[leftmargin=*]
\item ``you'' is your new method;
    \item ``two''  well-established methods (often NSGA-II and SPEA2),
    \item a ``next''  generation method e.g. MOEA/D~\cite{zhang2007moea}, NSGA-III~\cite{deb2014evolutionary},
    \item  one ``dumb'' baseline method (random search or SWAY).
\end{itemize}

@@

Along with increasing the confidence of a certain observation, it also increases the speed of research. For example, recently in FSE'17, Fu et al.~\cite{fu2017revisiting} described the effects of \textit{arxiv.org} or the open science effect. Fu et al. described how making the paper, and the replication packages results in 5 different techniques (each superior to its predecessor).\footnote{Please see \url{http://tiny.cc/unsup}  for more details on arxiv.org effect}

@@

  \noindent\textbf{Explanation: } SBSE is often instance-based and provide optimal or (near) optimal solutions. This is not ideal since it provides no insight into the problem. However, using SA techniques finding
building blocks of good solutions may shed light on the relationship
different parameters that affect the quality of a solution. This is an important shortcoming of SBSE which have not been addressed by this community. Valerdi
notes that, without automated tools, it can take days for human
experts to review just a few dozen examples. In that same
time, an automatic tool can explore thousands to billions of more
solutions. Humans can find it an overwhelming task just to
certify the correctness of conclusions generated from so many
results. Verrappa and Leiter warn that:
``... for industrial problems, these algorithms generate
(many) solutions which make the task of understanding
them and selecting one amongst them difficult
and time-consuming.''~\cite{veerappa2011understanding}. Currently, there has been only a few efforts to comprehend the results of an SBSE technique. Nair et al.~\cite{nair2017flash}
uses a \textit{domination tree} along with a Bayesian-based method to better, and more succinctly,
explain the search space.

 \noindent\textbf{Human in the loop: } Once we have explanation running, then the next step would be explore
combinations of human and artificial intelligence for
enhanced data-driven SBSE.
Standard
genetic algorithms must evaluate 1000s to 1,000,000s of examples-- which makes it hard for engineers or business users to debug or audit the results of that analysis. On the 
other hand, tools like FLASH (described in the last bullet)
and SWAY (see Section \ref{spl}) only evaluated $O(log(N))$ of the candidates-- which in practice can be just a few dozen examples. This number is small enough to ask humans
to watch the reasoning and, sometimes, catch the SBSE
tool making mistakes as it compares alternatives.  This style of human in the loop reasoning could be used for many tasks such as:
\begin{itemize}[leftmargin=*]
\item Debugging or auditing the reasoning.
\item Enhancing the reasoning; i.e. can human intelligence, applied judiciously,  boost artificial intelligence?
\item Checking for missing attributes: when human experts say two identical examples are different, we can infer that there are extra attributes, not currently being modeled, that are important.
\item Increasing human  confidence in the reasoning by tuning a seemingly complex black-box process into something
humans can monitor and understand.
\end{itemize}

@@

\section{Conclusions}
SE problems can be solved both by MSR and SBSE techniques, but both these methods have their shortcomings. This paper has argued these shortcomings can be overcome by merging ideas from both these domains, to give rise to a new field of software engineering called Data-Driven Search-based Software Engineering. This sub-area of software engineering boosts the techniques used in MSR and SBSE but drawing inspiration from the other field.
